Homework Report

### 2017-01-30 work/work.tex
Refactoring homework to report

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage[left=1in,right=1in,top=0.9in,bottom=0.9in]{geometry}
\usepackage{graphicx}
\usepackage{float}
\setlength\parindent{0pt}

\newtheorem*{definition}{Definition}
\newtheorem*{theorem}{Theorem}

@@

\section*{Heuristics}
In this report, I will use two vertex coloring heuristics as defined in class:
\begin{itemize}
\item \textbf{Heuristic A}: Greedy algorithm
\item \textbf{Heuristic B}: Greedy algorithm plus degree sequencing
\end{itemize}

Heuristic B is also known as the Welsh-Powell algorithm, which is defined in \cite{welsh}.

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.6]{graph-1.png}
\caption{Uncolored original graph \(G\)}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.6]{graph-2.png}
\caption{Coloring from applying heuristic B}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.6]{graph-3.png}
\caption{Optimal coloring of graph \(G\)}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.38]{graph-4.png}
\caption{Uncolored original graph \(H\)}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.38]{graph-5.png}
\caption{Worst-case coloring of \(H\) using either greedy heuristic}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.38]{graph-6.png}
\caption{Optimal coloring of \(H\)}
\end{figure}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage[left=1in,right=1in,top=0.9in,bottom=0.9in]{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{titling}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\setlength{\droptitle}{-1.5cm}
\setlength\parindent{0pt}

\makeatletter
\def\BState{\State\hskip-\ALG@thistlm}
\makeatother

\title{Homework Report}
\date{Last modified: \today}
\author{Shawn Seymour\\ University of Minnesota Morris}

\newtheorem*{definition}{Definition}
\newtheorem{prop}{Proposition}
\newtheorem*{theorem}{Theorem}

@@

\maketitle

\section*{Heuristics}
In this report, I will discuss multiple vertex coloring heuristics. I will define them as follows:

\subsection*{Heuristic A}

Heuristic A is the greedy algorithm. The input is a simple graph \(G = (V, E)\).

\begin{algorithm}
\caption{Greedy algorithm}
\begin{algorithmic}[1]
\State Label each vertex in $V$, i.e. $v_1, v_2, \dots, v_n$
\For{each $v \in V$}
\State Assign a color $p_i$ to $v_i$ using the smallest available $p_i$
\EndFor
\end{algorithmic}
\end{algorithm}

\subsection*{Heuristic B}

Heuristic B is the greedy algorithm with degree sequencing. It orders the vertices according to the decreasing value of their degree. This is also known as the Welsh-Powell algorithm, which is defined in \cite{welsh}.

\begin{algorithm}
\caption{Welsh-Powell algorithm}
\begin{algorithmic}[1]
\State Label each vertex in $V$, i.e. $v_1, v_2, \dots, v_n$, such that $d_G(v_1) \geq d_G(v_2) \geq \dots \geq d_G(v_n)$
\ForAll{$v \in V$}
\State Assign a color $p_i$ to $v_i$ using the smallest available $p_i$
\EndFor
\end{algorithmic}
\end{algorithm}

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.6]{images/graph-1.png}
\caption{Uncolored original graph \(G\)}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.6]{images/graph-2.png}
\caption{Coloring from applying heuristic B}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.6]{images/graph-3.png}
\caption{Optimal coloring of graph \(G\)}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.38]{images/graph-4.png}
\caption{Uncolored original graph \(H\)}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.38]{images/graph-5.png}
\caption{Worst-case coloring of \(H\) using either greedy heuristic}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.38]{images/graph-6.png}
\caption{Optimal coloring of \(H\)}
\end{figure}

\newpage
